Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2017-03-24 paper/presentation/DASFAA_presentation.tex
finish related works

%------------------------------
%page 4
\begin{frame}
\frametitle{Challenges (2/2)}	
Exploratory study on the on Edinburgh twitter corpus: 11/29 events contains less than 50 tweets.

@@

%\begin{comment}
%------------------------------
%page 5
\begin{frame}
\frametitle{How about existing methods on dealing with challenges?}

>>>>

%------------------------------
%page 4
\begin{frame}
\frametitle{Challenges (2/2)}	
Exploratory study on the \textit{Edinburgh twitter corpus}: 11/29 events contain less than 50 tweets.

@@

%\begin{comment}
%------------------------------
%page 5
\begin{frame}
\frametitle{How about existing methods? (1/2)}
Event detection methods \textit{without extra information}, such as
\begin{enumerate}
\item clustering articles
\begin{itemize}
	\item LSH[Petrovic, NAACL 2010]
	\item need to set threshold to determine whether new article represents a new event.
\end{itemize}
\item analyzing word frequencies
\begin{itemize}
	\item EDCoW[Weng, ICWSM 2011]
	\item treat the word as the basic unit in analysis, without regarding polysemy words (words have different meanings, e.g. ``apple")
\end{itemize}
\item finding bursty topics via topic modeling
\begin{itemize}
	\item TimeUserLDA[Diao, ACL 2012], BurstyBTM[Yan, AAAI 2015]
	\item detects the ``large" events but may ignore the ``small" ones. 
\end{itemize}
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{How about existing methods? (2/2)}
Event detection methods \textit{by leveraging extra information}
\begin{enumerate}
	\item typical one: Twevent[Li, CIKM 2012]
	\begin{itemize}
		\item divides the tweet into segments according to the Microsoft Web N-Gram service and Wikpedia
		\item detects the bursty segments and cluster these segments into candidate events
		\item still have to trade off between precision and recall
	\end{itemize}
\end{enumerate}
\end{frame}
